Viscous Transport in Eroding Porous Media

### 2019-10-09 docs/transport/erosion_transport.tex
NMM

\begin{abstract} 
  Transport of viscous fluid through porous media is a direct
  consequence of the pore structure. Here we investigate transport
  through specific two-dimensional porous geometries---those that are
  formed by fluid-mechanical erosion.  We investigate the tortuosity and
  dispersion by analyzing the first two statistical moments of tracer
  trajectories. For most geometries, the tortuosity decreases as erosion
  increases the porosity; however, interestingly, it is possible for
  erosion to increase the tortuosity. The simulated porosity-tortuosity
  relationships are compared with models available in the literature.
  Unsurprisingly, the asymptotic dispersion rate is also affected by the
  erosion process, but it is also affected by the number of and
  distribution of the eroding bodies.  Finally, we analyze the pore size
  distribution of an eroding geometry. The simulations are performed by
  combining a high-fidelity boundary integral equation solver for the
  fluid equations, a second-order stable time stepping method to
  simulate erosion, and new numerical methods to stably and accurately
  resolve nearly-touching eroded bodies and particle trajectories near
  the eroding bodies.

>>>>

\begin{abstract} 
  Transport of viscous fluid through porous media is a direct
  consequence of the pore structure. Here we investigate transport
  through \nick{a specific class of two-dimensional porous geometries, 
  namely those formed by fluid-mechanical erosion.}  
  We investigate the tortuosity and
  dispersion by analyzing the first two statistical moments of tracer
  trajectories. \nick{For most initial configurations, tortuosity decreases in time 
  as a result of erosion increasing the porosity. 
  However, we find that tortuosity can also increase transiently in certain cases.}
  \nick{The porosity-tortuosity relationships that result from our simulations 
  are compared against models available in the literature.}
  \nick{Asymptotic dispersion rates are also strongly affected by the
  erosion process, as well as by the number and
  distribution of the eroding bodies.}  
  Finally, we analyze the pore size
  distribution of an eroding geometry. The simulations are performed by
  combining a high-fidelity boundary integral equation solver for the
  fluid equations, a second-order stable time stepping method to
  simulate erosion, and new numerical methods to stably and accurately
  resolve nearly-touching eroded bodies and particle trajectories near
  the eroding bodies.
